{\bf {\Large Parameter sensitivity and identifiability for a biogeochemical model of hypoxia in the northern {G}ulf of {M}exico}}

### 2016-12-01 ident_manu.Rnw
percthresh fig added

The identifiability analyses suggested that many parameter subsets exceeded the thresholds of $\gamma = 10, 15$, providing further justification for using selection heuristics for parameter optimization.  Results for \ac{do} are provided first to demonstrate general concepts for the identifiability analyses, followed by an extension to the remaining state variables.  Parameter identifiability (as $\gamma$) for \ac{do} increased at different rates depending on the parameter category or the number of top parameters that were selected (\cref{fig:identplo}). By category, identifiability was lowest for all combinations of parameter subsets (from two to many parameters) in the phytoplankton (\Sexpr{catpersO2$Phytoplankton[1]}\% less than $\gamma = 15$, \Sexpr{catpersO2$Phytoplankton[2]}\% less than $\gamma = 10$) and zooplankton categories (\Sexpr{catpersO2$Zooplankton[1]}\%, less than $\gamma = 15$, \Sexpr{catpersO2$Zooplankton[2]}\%, less than $\gamma = 10$), whereas a all combinations were identifiable for optics (\Sexpr{catpersO2$Optics[1]}\%, less than $\gamma = 15$, \Sexpr{catpersO2$Optics[2]}\%, less than $\gamma = 10$) and a majority identifiable for organic matter (\Sexpr{catpersO2$`Organic Matter`[1]}\%, less than $\gamma = 15$, \Sexpr{catpersO2$`Organic Matter`[2]}\%, less than $\gamma = 10$) combinations were identifiable. Identifiability for parameters in the temperature category was not evaluated because \ac{do} was sensitive to only one parameter (i.e., $\gamma = 1$). Parameter combinations for choosing from the top, top two, top three, and top four parameters in each category together had decreasing identifability with the increasing size of the selection pool (e.g., top one versus top four parameters, \cref{fig:identplo}).  The percentage of parameter subsets that were below the acceptable thresholds for identifability was \Sexpr{toppersO2$top1[1]}\% less than $\gamma = 15$ and \Sexpr{toppersO2$top1[2]}\% less than $\gamma = 10$ for the top parameters in each category, \Sexpr{toppersO2$top2[1]}\% and \Sexpr{toppersO2$top2[2]}\% for the top two, \Sexpr{toppersO2$top3[1]}\% and \Sexpr{toppersO2$top3[2]}\% for the top three, and \Sexpr{toppersO2$top4[1]}\% and \Sexpr{toppersO2$top4[2]}\% for the fop four.

@@

%' Comparison of identifiability between categories showed that phytoplankton and zooplankton had the least identifiable parameter subsets.  As noted above, FishTank includes six phytoplankton and two zooplankton groups to characterize community structure and foodweb dynamics that likely have an important role in hypoxia development.  However, structural equations for each group do not vary considerably such that variation in parameter values primarily control differences between the groups, e.g., large-bodied vs small-bodied plankton, slow-growing vs. fast-growing plankton.  To obtain identifiability estimates of the plankton categories that were independent of groups, the identifiability analyses were re-evaluated using only one phytoplankton and one zooplankton group (\cref{fig:p1z1identbox}). Compared to all groups, evaluating a single group improved identifiability such that a majority of parameter combinations were below the threshold (\Sexpr{p1z1collcatpers$Phytoplankton[1]}\% less than $\gamma = 15$, \Sexpr{p1z1collcatpers$Phytoplankton[2]}\% less than $\gamma = 10$ for Phytoplankton; \Sexpr{p1z1collcatpers$Zooplankton[1]}\%, less than $\gamma = 15$, \Sexpr{p1z1collcatpers$Zooplankton[2]}\%, less than $\gamma = 10$ for zooplankton).  Analysis of identifiability for top parameters in all categories did not show similar changes in identifiability.  Although all combinations for the top one, two, and three parameters in each category were still well below the threshold, selecting the top four and five parameters showed an increase (\Sexpr{p1z1colltoppers$top4[1]}\% less than $\gamma = 15$, \Sexpr{p1z1colltoppers$top4[2]}\% less than $\gamma = 10$) and a decrease (\Sexpr{p1z1colltoppers$top5[1]}\% less than $\gamma = 15$, \Sexpr{p1z1colltoppers$top5[2]}\% less than $\gamma = 10$) in identifiability, respectively (\cref{fig:p1z1identbox}), compared to results that included all phytoplankton and zooplankton groups (\cref{fig:identbox}).  

@@

>>>>

The identifiability analyses suggested that many parameter subsets exceeded the thresholds of $\gamma = 10, 15$, providing further justification for using selection heuristics for parameter optimization.  Results for \ac{do} are provided first to demonstrate general concepts for the identifiability analyses, followed by an extension to the remaining state variables.  Parameter identifiability (as $\gamma$) for \ac{do} increased at different rates with increasing size of parameter subsets depending on the parameter category or the number of top parameters that were selected (\cref{fig:identplo}). By category, identifiability was lowest for all combinations of parameter subsets (from two to many parameters) in the phytoplankton (\Sexpr{catpersO2$Phytoplankton[1]}\% less than $\gamma = 15$, \Sexpr{catpersO2$Phytoplankton[2]}\% less than $\gamma = 10$) and zooplankton categories (\Sexpr{catpersO2$Zooplankton[1]}\% less than $\gamma = 15$, \Sexpr{catpersO2$Zooplankton[2]}\% less than $\gamma = 10$), whereas a all combinations were identifiable for optics (\Sexpr{catpersO2$Optics[1]}\% less than $\gamma = 15$, \Sexpr{catpersO2$Optics[2]}\% less than $\gamma = 10$) and a majority identifiable for organic matter (\Sexpr{catpersO2$`Organic Matter`[1]}\% less than $\gamma = 15$, \Sexpr{catpersO2$`Organic Matter`[2]}\% less than $\gamma = 10$) combinations were identifiable. Identifiability for parameters in the temperature category was not evaluated because \ac{do} was sensitive to only one parameter (i.e., $\gamma = 1$). Parameter combinations for choosing from the top, top two, top three, and top four parameters in each category together had decreasing identifability with the increasing size of the selection pool (e.g., top one versus top four parameters, \cref{fig:identplo}).  The percentage of parameter subsets that were below the acceptable thresholds for identifability was \Sexpr{toppersO2$top1[1]}\% less than $\gamma = 15$ and \Sexpr{toppersO2$top1[2]}\% less than $\gamma = 10$ for the top parameters in each category, \Sexpr{toppersO2$top2[1]}\% and \Sexpr{toppersO2$top2[2]}\% for the top two, \Sexpr{toppersO2$top3[1]}\% and \Sexpr{toppersO2$top3[2]}\% for the top three, and \Sexpr{toppersO2$top4[1]}\% and \Sexpr{toppersO2$top4[2]}\% for the fop four.  Results for the remaining state variables had similar patterns in identifability with increasing size of parameter subsets and selection categories, although differences in identifiabiltiy between state variables was observed (\cref{fig:identploall}).  Most notably, nitrate was consistently the least identifiable variable for all selection heuristics (highest $\gamma$), whereas \ac{do} was most identifiable.

@@

%' Comparison of identifiability between categories showed that phytoplankton and zooplankton had the least identifiable parameter subsets.  As noted above, FishTank includes six phytoplankton and two zooplankton groups to characterize community structure and foodweb dynamics that likely have an important role in hypoxia development.  However, structural equations for each group do not vary considerably such that variation in parameter values primarily control differences between the groups, e.g., large-bodied vs small-bodied plankton, slow-growing vs. fast-growing plankton.  To obtain identifiability estimates of the plankton categories that were independent of groups, the identifiability analyses were re-evaluated using only one phytoplankton and one zooplankton group (\cref{fig:p1z1identbox}). Compared to all groups, evaluating a single group improved identifiability such that a majority of parameter combinations were below the threshold (\Sexpr{p1z1collcatpers$Phytoplankton[1]}\% less than $\gamma = 15$, \Sexpr{p1z1collcatpers$Phytoplankton[2]}\% less than $\gamma = 10$ for Phytoplankton; \Sexpr{p1z1collcatpers$Zooplankton[1]}\% less than $\gamma = 15$, \Sexpr{p1z1collcatpers$Zooplankton[2]}\% less than $\gamma = 10$ for zooplankton).  Analysis of identifiability for top parameters in all categories did not show similar changes in identifiability.  Although all combinations for the top one, two, and three parameters in each category were still well below the threshold, selecting the top four and five parameters showed an increase (\Sexpr{p1z1colltoppers$top4[1]}\% less than $\gamma = 15$, \Sexpr{p1z1colltoppers$top4[2]}\% less than $\gamma = 10$) and a decrease (\Sexpr{p1z1colltoppers$top5[1]}\% less than $\gamma = 15$, \Sexpr{p1z1colltoppers$top5[2]}\% less than $\gamma = 10$) in identifiability, respectively (\cref{fig:p1z1identbox}), compared to results that included all phytoplankton and zooplankton groups (\cref{fig:identbox}).  

@@

% percent below gamma thresholds
<<percthresh, eval = T, fig.cap = 'Percent of identifiable parameter sets for \\ac{do} at different $\\gamma$ thresholds, selection criteria, and total number of parameters in the set.  Thresholds varied from $\\gamma = 2$ to $20$ such that sets with $\\gamma$ below a threshold were considered identifiable relative to the value. Plots in (a) show percent of identifiable sets by selecting parameters within categories and (b) shows percent identifiable by selecting from the top 1 through 4 parameters in all categories.  Percent identifiable was based on all sets in \\cref{fig:identplo}.', fig.height = 8, fig.width = 9, echo = F, cache = TRUE>>=
data(cat_ident_all)
data(top_ident_all)

# state variable, categories (no temp ident because only one parameter)
catnms <- c('Optics', 'Organic Matter', 'Phytoplankton', 'Zooplankton')
toplevs <- paste0('top', 1:4)
toplabs <- paste('Top', 1:4)
stts_lev <- c('O2')
stts_lab <- c('Dissolved Oxygen')

thresh <- seq(2, 20, by = 2)

# percent combos less than gamma 15, 10 by state variable, by parameter category
# temperature category not evaluated, only one paramaeter
collcatpers <- lapply(cat_ident_all[stts_lev], function(stvar){

  bystvar <- lapply(stvar[!names(stvar) %in% 'Temperature'], function(x){

    bysets <- split(x, x$N) %>% 
      lapply(function(sets){
        colls <- sets$coll
        sapply(thresh, function(x) 100 * sum(colls < x)/length(colls))

      }) %>% 
      do.call('rbind', .) %>% 
      data.frame(
        nparms = row.names(.), 
        .
      ) %>% 
      mutate(
        nparms = as.numeric(as.character(nparms))
      ) %>% 
      gather('lval', 'perc', -nparms) %>% 
      mutate(lval = factor(lval, 
        levels = paste0('X', 1:length(thresh)), 
        labels = paste0('l', thresh)
      ))
    bysets

  }) %>% 
  reshape2::melt(., id.vars = names(.[[1]])) %>% 
  rename(Category = L1)

  return(bystvar)

  }) %>% 
  reshape2::melt(., id.vars = names(.[[1]])) %>% 
  rename(`State variable` = L1) %>% 
  mutate(
    `State variable` = factor(`State variable`, levels = stts_lev, labels = stts_lab),
    Category = factor(Category, levels = catnms), 
    Threshold = gsub('^l', '', lval),
    Threshold = as.numeric(Threshold)
    )

colltoppers <- lapply(top_ident_all[stts_lev], function(stvar){

  bystvar <- lapply(stvar, function(x){

    bysets <- split(x, x$N) %>% 
      lapply(function(sets){
        colls <- sets$coll
        sapply(thresh, function(x) 100 * sum(colls < x)/length(colls))

      }) %>% 
      do.call('rbind', .) %>% 
      data.frame(
        nparms = row.names(.), 
        .
      ) %>% 
      mutate(
        nparms = as.numeric(as.character(nparms))
      ) %>% 
      gather('lval', 'perc', -nparms) %>% 
      mutate(lval = factor(lval, 
        levels = paste0('X', 1:length(thresh)), 
        labels = paste0('l', thresh)
      ))
    bysets

  }) %>% 
  reshape2::melt(., id.vars = names(.[[1]])) %>% 
  rename(Category = L1) %>% 
  filter(!Category %in% 'top5')

  return(bystvar)

  }) %>% 
  reshape2::melt(., id.vars = names(.[[1]])) %>% 
  rename(`State variable` = L1) %>% 
  mutate(
    `State variable` = factor(`State variable`, levels = stts_lev, labels = stts_lab),
    Category = factor(Category, levels = toplevs, labels = toplabs), 
    Threshold = gsub('^l', '', lval),
    Threshold = as.numeric(Threshold)
    )

toplo1 <- collcatpers
toplo2 <- colltoppers

# default theme
mytheme <- theme_minimal() + 
  theme(
    axis.line.x = element_line(), 
    axis.line.y = element_line(), 
    axis.title.x = element_blank(), 
    axis.title.y = element_blank(),
    axis.ticks.x = element_line(),
    axis.ticks.y = element_line(),
    axis.ticks.length = unit(.1, "cm"), 
    legend.position = 'none'
  )

p1 <- ggplot(toplo1, aes(x = nparms, group = lval)) + 
  geom_line(aes(y = perc), colour = lncol) + 
  geom_point(aes(y = perc, fill = Threshold), shape = 21, colour = lncol, 
    size = sz
    ) + 
  scale_fill_distiller(palette = "Spectral") +
  facet_wrap(~ Category, ncol = 1) +
  mytheme +
  ggtitle('(a) By parameter category')

p2 <- ggplot(toplo2, aes(x = nparms, group = lval)) + 
  geom_line(aes(y = perc), colour = lncol) + 
  geom_point(aes(y = perc, fill = Threshold), shape = 21, colour = lncol, 
    size = sz
    ) + 
  scale_fill_distiller(palette = "Spectral") +
  facet_wrap(~ Category, ncol = 1) +
  mytheme +
  ggtitle('(b) By top parameters, all categories')

pleg <- ggplot(toplo2, aes(x = nparms, group = lval)) + 
  geom_point(aes(y = perc, fill = Threshold)) + 
  scale_fill_distiller(palette = "Spectral")
pleg <- g_legend(pleg)

grid.arrange(
  arrangeGrob(p1, p2, ncol = 2, bottom = 'Parameters in set'),
  left = 'Percent identifiable sets',
  pleg, ncol = 2, widths = c(1, 0.2)
)
@

### 2016-12-01 ident_manu.tex
percthresh fig added

\begin{singlespace}
\title{{\bf {\Large Parameter sensitivity and identifiability for a biogeochemical model of hypoxia in the northern {G}ulf of {M}exico}}}
\author{
  {\bf {\normalsize Marcus W. Beck$^1$, John C. Lehrter$^2$, Lisa L. Lowe$^3$}}
  \\\\{\textit {\normalsize $^1$USEPA National Health and Environmental Effects Research Laboratory}}
  \\{\textit {\normalsize Gulf Ecology Division, 1 Sabine Island Drive, Gulf Breeze, FL 32561}}
	\\{\textit {\normalsize Phone: 850-934-2480, Fax: 850-934-2401}}
	\\{\textit {\normalsize Email: \href{mailto:beck.marcus@epa.gov}{beck.marcus@epa.gov}}}
	  \\\\{\textit {\normalsize $^2$Dauphin Island Sea Lab, University of South Alabama}}
  \\{\textit {\normalsize Dauphin Island, AL 36528}}
	\\{\textit {\normalsize Phone: 251-861-2141 ext. 7567}}
	\\{\textit {\normalsize Email: \href{mailto:jlehrter@disl.org}{jlehrter@disl.org}}}
	\\\\{\textit {\normalsize $^3$Lockheed Martin IS \& GS - Civil, supporting the USEPA}}
	\\{\textit {\normalsize Resarch Triangle Park, NC 27709}}
	\\{\textit {\normalsize Phone: 919-541-3985,}}
	\\{\textit {\normalsize Email: \href{mailto:lowe.lisa@epa.gov}{lowe.lisa@epa.gov}}}
  \vspace{1in} 
  \\ Version Date:   Wed Nov 30 14:30:44 2016 -0600
	}
\date{}
\maketitle
\end{singlespace}
\clearpage

@@

The identifiability analyses suggested that many parameter subsets exceeded the thresholds of $\gamma = 10, 15$, providing further justification for using selection heuristics for parameter optimization.  Results for \ac{do} are provided first to demonstrate general concepts for the identifiability analyses, followed by an extension to the remaining state variables.  Parameter identifiability (as $\gamma$) for \ac{do} increased at different rates depending on the parameter category or the number of top parameters that were selected (\cref{fig:identplo}). By category, identifiability was lowest for all combinations of parameter subsets (from two to many parameters) in the phytoplankton ($60$\% less than $\gamma = 15$, $43$\% less than $\gamma = 10$) and zooplankton categories ($53.1$\%, less than $\gamma = 15$, $40$\%, less than $\gamma = 10$), whereas a all combinations were identifiable for optics ($100$\%, less than $\gamma = 15$, $100$\%, less than $\gamma = 10$) and a majority identifiable for organic matter ($91.9$\%, less than $\gamma = 15$, $76.5$\%, less than $\gamma = 10$) combinations were identifiable. Identifiability for parameters in the temperature category was not evaluated because \ac{do} was sensitive to only one parameter (i.e., $\gamma = 1$). Parameter combinations for choosing from the top, top two, top three, and top four parameters in each category together had decreasing identifability with the increasing size of the selection pool (e.g., top one versus top four parameters, \cref{fig:identplo}).  The percentage of parameter subsets that were below the acceptable thresholds for identifability was $100$\% less than $\gamma = 15$ and $100$\% less than $\gamma = 10$ for the top parameters in each category, $90.6$\% and $80.7$\% for the top two, $80.7$\% and $70.9$\% for the top three, and $55.8$\% and $45.7$\% for the fop four.

@@

%' Comparison of identifiability between categories showed that phytoplankton and zooplankton had the least identifiable parameter subsets.  As noted above, FishTank includes six phytoplankton and two zooplankton groups to characterize community structure and foodweb dynamics that likely have an important role in hypoxia development.  However, structural equations for each group do not vary considerably such that variation in parameter values primarily control differences between the groups, e.g., large-bodied vs small-bodied plankton, slow-growing vs. fast-growing plankton.  To obtain identifiability estimates of the plankton categories that were independent of groups, the identifiability analyses were re-evaluated using only one phytoplankton and one zooplankton group (\cref{fig:p1z1identbox}). Compared to all groups, evaluating a single group improved identifiability such that a majority of parameter combinations were below the threshold (p1z1collcatpers$Phytoplankton[1]\% less than $\gamma = 15$, p1z1collcatpers$Phytoplankton[2]\% less than $\gamma = 10$ for Phytoplankton; p1z1collcatpers$Zooplankton[1]\%, less than $\gamma = 15$, p1z1collcatpers$Zooplankton[2]\%, less than $\gamma = 10$ for zooplankton).  Analysis of identifiability for top parameters in all categories did not show similar changes in identifiability.  Although all combinations for the top one, two, and three parameters in each category were still well below the threshold, selecting the top four and five parameters showed an increase (p1z1colltoppers$top4[1]\% less than $\gamma = 15$, p1z1colltoppers$top4[2]\% less than $\gamma = 10$) and a decrease (p1z1colltoppers$top5[1]\% less than $\gamma = 15$, p1z1colltoppers$top5[2]\% less than $\gamma = 10$) in identifiability, respectively (\cref{fig:p1z1identbox}), compared to results that included all phytoplankton and zooplankton groups (\cref{fig:identbox}).  

@@

>>>>

\begin{singlespace}
\title{{\bf {\Large Parameter sensitivity and identifiability for a biogeochemical model of hypoxia in the northern {G}ulf of {M}exico}}}
\author{
  {\bf {\normalsize Marcus W. Beck$^1$, John C. Lehrter$^2$, Lisa L. Lowe$^3$}}
  \\\\{\textit {\normalsize $^1$USEPA National Health and Environmental Effects Research Laboratory}}
  \\{\textit {\normalsize Gulf Ecology Division, 1 Sabine Island Drive, Gulf Breeze, FL 32561}}
	\\{\textit {\normalsize Phone: 850-934-2480, Fax: 850-934-2401}}
	\\{\textit {\normalsize Email: \href{mailto:beck.marcus@epa.gov}{beck.marcus@epa.gov}}}
	  \\\\{\textit {\normalsize $^2$Dauphin Island Sea Lab, University of South Alabama}}
  \\{\textit {\normalsize Dauphin Island, AL 36528}}
	\\{\textit {\normalsize Phone: 251-861-2141 ext. 7567}}
	\\{\textit {\normalsize Email: \href{mailto:jlehrter@disl.org}{jlehrter@disl.org}}}
	\\\\{\textit {\normalsize $^3$Lockheed Martin IS \& GS - Civil, supporting the USEPA}}
	\\{\textit {\normalsize Resarch Triangle Park, NC 27709}}
	\\{\textit {\normalsize Phone: 919-541-3985,}}
	\\{\textit {\normalsize Email: \href{mailto:lowe.lisa@epa.gov}{lowe.lisa@epa.gov}}}
  \vspace{1in} 
  \\ Version Date:   Wed Nov 30 17:02:50 2016 -0600
	}
\date{}
\maketitle
\end{singlespace}
\clearpage

@@

The identifiability analyses suggested that many parameter subsets exceeded the thresholds of $\gamma = 10, 15$, providing further justification for using selection heuristics for parameter optimization.  Results for \ac{do} are provided first to demonstrate general concepts for the identifiability analyses, followed by an extension to the remaining state variables.  Parameter identifiability (as $\gamma$) for \ac{do} increased at different rates with increasing size of parameter subsets depending on the parameter category or the number of top parameters that were selected (\cref{fig:identplo}). By category, identifiability was lowest for all combinations of parameter subsets (from two to many parameters) in the phytoplankton ($60$\% less than $\gamma = 15$, $43$\% less than $\gamma = 10$) and zooplankton categories ($53.1$\% less than $\gamma = 15$, $40$\% less than $\gamma = 10$), whereas a all combinations were identifiable for optics ($100$\% less than $\gamma = 15$, $100$\% less than $\gamma = 10$) and a majority identifiable for organic matter ($91.9$\% less than $\gamma = 15$, $76.5$\% less than $\gamma = 10$) combinations were identifiable. Identifiability for parameters in the temperature category was not evaluated because \ac{do} was sensitive to only one parameter (i.e., $\gamma = 1$). Parameter combinations for choosing from the top, top two, top three, and top four parameters in each category together had decreasing identifability with the increasing size of the selection pool (e.g., top one versus top four parameters, \cref{fig:identplo}).  The percentage of parameter subsets that were below the acceptable thresholds for identifability was $100$\% less than $\gamma = 15$ and $100$\% less than $\gamma = 10$ for the top parameters in each category, $90.6$\% and $80.7$\% for the top two, $80.7$\% and $70.9$\% for the top three, and $55.8$\% and $45.7$\% for the fop four.  Results for the remaining state variables had similar patterns in identifability with increasing size of parameter subsets and selection categories, although differences in identifiabiltiy between state variables was observed (\cref{fig:identploall}).  Most notably, nitrate was consistently the least identifiable variable for all selection heuristics (highest $\gamma$), whereas \ac{do} was most identifiable.

@@

%' Comparison of identifiability between categories showed that phytoplankton and zooplankton had the least identifiable parameter subsets.  As noted above, FishTank includes six phytoplankton and two zooplankton groups to characterize community structure and foodweb dynamics that likely have an important role in hypoxia development.  However, structural equations for each group do not vary considerably such that variation in parameter values primarily control differences between the groups, e.g., large-bodied vs small-bodied plankton, slow-growing vs. fast-growing plankton.  To obtain identifiability estimates of the plankton categories that were independent of groups, the identifiability analyses were re-evaluated using only one phytoplankton and one zooplankton group (\cref{fig:p1z1identbox}). Compared to all groups, evaluating a single group improved identifiability such that a majority of parameter combinations were below the threshold (p1z1collcatpers$Phytoplankton[1]\% less than $\gamma = 15$, p1z1collcatpers$Phytoplankton[2]\% less than $\gamma = 10$ for Phytoplankton; p1z1collcatpers$Zooplankton[1]\% less than $\gamma = 15$, p1z1collcatpers$Zooplankton[2]\% less than $\gamma = 10$ for zooplankton).  Analysis of identifiability for top parameters in all categories did not show similar changes in identifiability.  Although all combinations for the top one, two, and three parameters in each category were still well below the threshold, selecting the top four and five parameters showed an increase (p1z1colltoppers$top4[1]\% less than $\gamma = 15$, p1z1colltoppers$top4[2]\% less than $\gamma = 10$) and a decrease (p1z1colltoppers$top5[1]\% less than $\gamma = 15$, p1z1colltoppers$top5[2]\% less than $\gamma = 10$) in identifiability, respectively (\cref{fig:p1z1identbox}), compared to results that included all phytoplankton and zooplankton groups (\cref{fig:identbox}).  

@@

% percent below gamma thresholds
\begin{figure}[!ht]

{\centering \includegraphics[width=\maxwidth]{figs/percthresh-1}

\caption{Percent of identifiable parameter sets for \ac{do} at different $\gamma$ thresholds, selection criteria, and total number of parameters in the set.  Thresholds varied from $\gamma = 2$ to $20$ such that sets with $\gamma$ below a threshold were considered identifiable relative to the value. Plots in (a) show percent of identifiable sets by selecting parameters within categories and (b) shows percent identifiable by selecting from the top 1 through 4 parameters in all categories.  Percent identifiable was based on all sets in \cref{fig:identplo}.}\label{fig:percthresh}
\end{figure}
